Topic Scores

### 2019-02-19 test_delete_later_sofia.Rmd
topic contribution to course

student <- list()
student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war") #sample(terms, 5)
student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
```

@@

#
##key word Contributions to Topic
 contribution_to_topics <- beta_description$k35                       %>%
  filter(term %in% student$kw_policy)       %>%
  arrange(topic, desc(beta))                %>%
  spread(key=topic, value=beta)             %>%
  mutate_at(.vars = vars(num_range("Topic ",1:35)),
            .funs = standardize)

@@

##Topic contribution to course
```{r course_score}

#
## Topic contribution to course
gamma_descriptions$k35     %>%
  full_join(student$topic_score, by = "topic") %>%
  group_by(document, topic)                           %>%
  summarise(total_gamma= sum(gamma))
  mutate(X = gamma * B_proportion)             %>%
  group_by(document)                           %>%
  summarise(course_score = sum(X))             %>%
  arrange(desc(course_score))                  %>%
  left_join(
    select(d_course, `Course ID`, `Course Title`),
    by = c("document" = "Course ID")
    )

>>>>

student <- list()
student$kw_policy <- c("international", "economic", "conflict", "develop", "policy", "war", "philosophy") #sample(terms, 5)
student$kw_climate <- c("climate", "sustainability", "change", "development", "develop","sustain", "sustainable") #sample(terms, 5)
```

@@

#
##key word Contributions to Topic
 contribution_to_topics <- beta_description$k35                       %>%
  filter(term %in% student$kw_policy)                                 %>%
  arrange(topic, desc(beta))                                          %>%
  spread(key=topic, value=beta)                                       %>%
  mutate_at(.vars = vars(num_range("Topic ",1:35)),
            .funs = standardize)                                      %>%
   gather(key = "topic", value = "beta_rank", num_range("Topic ", 1:35))

@@

##Topic contribution to course
```{r course_score}
#
##Extracts recommended courses
my_courses <- top_n(x = student$course_score, n = 5, wt =course_score) %>% 
  pull(document)

#
## Topic contribution to course
key_words <- gamma_descriptions$k35                             %>%
  filter(document %in% my_courses)                 %>%
  arrange(document, gamma)                         %>%
  full_join(contribution_to_topics, by = "topic" ) %>%
  arrange(document, desc(gamma), desc(beta_rank) ) %>%
  group_by(document #, 
           #gamma
           )                                       %>%
  filter(row_number() %in% 1:3)                    %>%  #makes most sense with just 1 kw # group_by(document) %>% filter(row_number() %in% 1:9) 
  group_by(document)                               %>%
  summarise(key_words = list(Reduce(f= c,
                               x = term)))
